Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-10 paper/manuscript.tex
Updates from Overleaf

The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in their substituents; e.g. consider a transformation of benzene (A) to benzyl alcohol (B) fig.~\ref{fig:fig4_topology}.

@@

Thus, in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works. 

@@

    \caption{\textbf{Two common topologies for AFE calculations}left: A single topology uses softcore potentials to convert from one type of atom to an other. Dummy atoms (Du) are used when there is no corresponding maximum common substructure match between the two molecules for certain atoms. right: The dual topology does not convert one species to another, but only converts between Du atoms and an interacting species, but usually uses softcore potentials for this. The 'mixed' intermediate atoms are used in both dual and single topology approaches. Only the way the transformation occurs and the end states differ. Following the arrow along the left and right illustrate the differences.  Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}

>>>>

The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in their substituents; e.g. consider a transformation of benzene (A) to benzyl alcohol (B) fig.~\ref{fig:topology}.

@@

Thus, in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in left arm of fig.~\ref{fig:fig_topology}. 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig_topology}'s right branch depicts how such a dual topology works. 

@@

    \caption{\textbf{Two common topologies for AFE calculations} left: A single topology uses softcore potentials to convert from one type of atom to an other. Dummy atoms (Du) are used when there is no corresponding maximum common substructure match between the two molecules for certain atoms. right: The dual topology does not convert one species to another, but only converts between Du atoms and an interacting species, but usually uses softcore potentials for this. The 'mixed' intermediate atoms are used in both dual and single topology approaches. Only the way the transformation occurs and the end states differ. Following the arrow along the left and right illustrate the differences.  Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
